### 2023-08-08 chapter_2/src/appendix.qmd
update citations and fix a couple of typos

I posted a pre-registration of my hypotheses [on OSF.](https://osf.io/e9gk8/) The pre-registration allows me to offer transparency about what I expect to find before I analyze any data. This reduces the amount of post-hoc rationalization of any findings pulled from the data. The pre-registered hypotheses are the same as those that are tested here. Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing. In the spirit of complete transparancy, I wanted to make a note of these differences.

@@

To confirm that these models return sensical predictions, I again plot the posterior predictions. @fig-h-3-ppc seems to suggest that both models do a pretty good job at returning a distribution fo predicted outcomes in terms of differences between those values and outcomes measured in my sample.

@@

As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design. The outcome is a continous and bounded variable between the value of 0 and 1. I note in the main text that I use a ordered beta regression, but here I provide more specifics. As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continous variable with no finite bounding as I would with a OLS would be inappropriate. To ensure that I am using the most appropriate estimator to explain the outcome of interest, I elect to use an ordered beta regression. Beta regression models are a type of distributional model that essentially tries to model the distribution of the outcome variable. The standard beta regression model can fit models where the outcome is (0, 1). However, my outcome is [0, 1). I could elect to use a zero-inflated beta regression which would allow me to appropriately model this outcome. However, @kubinec_2022_pa demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1.

The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_2022_pa] package that I use to fit the model. However, I receive warnings indicating that there are divergent transitions. For HMC, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution. As I note in the main text of the book, I am using a multilevel model that includes a partially pooled parameter for the districts and use two non-pooled parameters for the state and the election year. This is a pretty complex problem. Especially givent the estimator that I am using here. More troubling still is that my $\hat{R}$ values are not equal to 1 for either model. These two things together suggest that there is a pretty serious problem and that my posterior distributions are quite unstable.

>>>>

I posted a pre-registration of my hypotheses [on OSF.](https://osf.io/e9gk8/) The pre-registration allows me to offer transparency about what I expect to find before I analyze any data. This reduces the amount of post-hoc rationalization of any findings pulled from the data. The pre-registered hypotheses are the same as those that are tested here. Despite the similarities between my pre-registered hypotheses and research design, there are a few subtle differences between what I pre-registered and what I ended up doing. In the spirit of complete transparency, I wanted to make a note of these differences.

@@

To confirm that these models return logical predictions, I again plot the posterior predictions. @fig-h-3-ppc seems to suggest that both models do a pretty good job at returning a distribution fo predicted outcomes in terms of differences between those values and outcomes measured in my sample.

@@

As I mention in the main text of the book, I note that I regress the 5-year rolling average of the democratic vote share in a state upon the proportion of the color red and blue on the yard signs downloaded from the Center for American Political Design. The outcome is a continuous and bounded variable between the value of 0 and 1. I note in the main text that I use a ordered beta regression, but here I provide more specifics. As the outcome is continuous but bounded between 0 and 1, treating the outcome variable as a continuous variable with no finite bounding as I would with a OLS would be inappropriate. To ensure that I am using the most appropriate estimator to explain the outcome of interest, I elect to use an ordered beta regression. Beta regression models are a type of distributional model that essentially tries to model the distribution of the outcome variable. The standard beta regression model can fit models where the outcome is (0, 1). However, my outcome is [0, 1). I could elect to use a zero-inflated beta regression which would allow me to appropriately model this outcome. However, @kubinec_ordered_2022 demonstrates that the ordered beta regression is a much more efficient and accurate (in terms of a number of various metrics) approach to dealing with outcomes that can equal either 0 or 1.

The default priors for $\beta_i$ is $N(0, 5)$ in the $ordbetareg$ [@kubinec_ordered_2022] package that I use to fit the model. However, I receive warnings indicating that there are divergent transitions. For HMC, divergent transitions indicate that the sampler is having problems with the curvature of your posterior distribution. As I note in the main text of the book, I am using a multilevel model that includes a partially pooled parameter for the districts and use two non-pooled parameters for the state and the election year. This is a pretty complex problem. Especially givent the estimator that I am using here. More troubling still is that my $\hat{R}$ values are not equal to 1 for either model. These two things together suggest that there is a pretty serious problem and that my posterior distributions are quite unstable.
